I am working on the filtering portion of this project. This has involved configuring Snort and getting familiar with it. I have been reading through the Snort manual so that I can understanding the necessary Snort configuration settings. The idea is to use Snort as a way of blocking TCP connections to unauthorized IP addresses. From my initial testing, Snort seems to be too slow to block all connections. For long TCP connections (such as downloading a picture), Snort works. For short TCP connections (such as downloading HTML for a website), Snort is too slow to react to block the connection.

My goal for last week was to have Snort figured out and blocking connections to IP addresses, which I have not completed yet. I was not expecting Snort to have problems with blocking the connection. I have had to do some digging around to see what is going on, such as looking at Wireshark traces.

For next week, I plan on figuring out why Snort is not responding quick enough. It might be a configuration error on my part, the computer I am running Snort on might not be fast enough, or it could be that Snort is not able to do what we need it to do. If that is the case, I will look into other options for blocking TCP connections.


@article{holloway2013zero,
  title={Zero to eight: young children and their internet use},
  author={Holloway, Donell and Green, Lelia and Livingstone, Sonia},
  year={2013},
  publisher={EU Kids Online Network}
}

@article{livingstone2008parental,
  title={Parental mediation of children's internet use},
  author={Livingstone, Sonia and Helsper, Ellen J},
  journal={Journal of broadcasting \& electronic media},
  volume={52},
  number={4},
  pages={581--599},
  year={2008},
  publisher={Taylor \& Francis}
}
